---
format: 
  html:
    page-layout: custom
    theme: 
      - simplex
      - custom.scss
    mainfont: sans-serif
    toc: false
    minimal: true
    embed-resources: true
execute: 
  echo: false
  error: false
  warning: false
  output: asis
---

```{r}
#| include: false
library(googlesheets4, include.only = "read_sheet")
source("utils.R")
```

```{css}
body, 
section {
  background-color: white;
}

.about-list iconify-icon {
  color: #533B4D;
}

#profile {
  width: 100%;
  margin: 0;
  padding: 0;
}

footer.footer {
  display: none;
}

a {
  text-decoration: none;
}

h2,
h3,
h4,
h5 {
  break-after: avoid;  
}

h1 {
  margin-top: 0;
}

h2 {
  margin-top: 2rem !important;
}

h3, 
h4, 
h5 {
  margin-top: 1rem !important;
}

h3 {
  font-size: 1.3rem;
  font-style: italic;
}

section.level1 {
  padding-top: 0;
}

/* suppress margins at the top of the page */
section.level2:first-child h2:first-child,
section.level3:first-child h3:first-child,
section.level4:first-child h4:first-child,
.bib-list:first-child .bib-year:first-child h3:first-child {
  margin-top: 0 !important;
}

.bib-list .bib-year h3 {
  break-after: avoid;
}

.bib-list .bib-year .bib-block {
  break-inside: avoid;
}

.bib-list .bib-year .bib-block:not(:first-of-type){
  margin-top: 1rem;
}

.bib-list .bib-year .bib-block .bib-buttons {
  display: none;
}

#profile span.icon {
  display: inline-block;
  width: 1.2rem;
  text-align: center;
}

@page {
  size: letter portrait;
  margin: 0.8in;
  font-size: 1rem;
  background-color: white;
}
```

# Kenneth Blake Vernon

:::::: {.grid .align-items-start #profile}
::: {.g-col-8}
[**Scientific Computing and Imaging Institute**](https://www.sci.utah.edu/people/k.vernon.html)  
University of Utah  
72 So. Central Campus Drive Room 3750  
Salt Lake City, Utah 84112  
:::

::: {.g-col-4 .text-end}
[kbvernon.io](https://www.kbvernon.io/) [{{< iconify fa6-solid:image-portrait >}}]{.icon}  
[kbvernon](https://github.com/kbvernon) [{{< iconify fa:github >}}]{.icon}  
[0000-0003-0098-5092](https://orcid.org/0000-0003-0098-5092) [{{< iconify academicons:orcid >}}]{.icon}  
[2PE4za4AAAAJ](https://scholar.google.com/citations?user=2PE4za4AAAAJ&hl=en) [{{< iconify academicons:google-scholar >}}]{.icon}
:::
::::::

## {{< iconify fa6-solid:briefcase >}} Professional Appointments

::: {.about-list}
-   **One-U Responsible AI Postdoctoral Fellow** | 2025-Present  
    Scientific Computing and Imaging Institute  
    School of Environment, Society, and Sustainability  
    University of Utah  
-   **Post-Doctoral Associate** | 2022-2024  
    Center for Collaborative Synthesis in Archaeology, CU Boulder  
-   **Assistant Director** | 2018-2022  
    University of Utah Archaeological Center  
:::

## {{< iconify fa6-solid:graduation-cap >}} Education

::: {.about-list}
-   **University of Utah** | Salt Lake City, UT  
    PhD in Anthropology, 2022  
-   **Northern Illinois University** | DeKalb, IL  
    MA in Philosophy, 2009  
-   **University of Central Arkansas** | Conway, AR  
    BA in History and Philosophy, 2006  
:::

## {{< iconify fa6-solid:book >}} Publications

### Peer-reviewed journal articles

```{r}
#| label: articles
articles <- get_collection(
  user = Sys.getenv("ZOTERO_ID"),
  key = Sys.getenv("ZOTERO_KEY"),
  collection = Sys.getenv("ZOTERO_ARTICLE")
)

bib_list(articles, "article")
```

### Manuscripts

```{r}
#| label: manuscripts
manuscripts <- get_collection(
  user = Sys.getenv("ZOTERO_ID"),
  key = Sys.getenv("ZOTERO_KEY"),
  collection = Sys.getenv("ZOTERO_MANUSCRIPT")
)

bib_list(manuscripts, "manuscript")
``` 

### Book reviews

```{r}
#| label: reviews
reviews <- get_collection(
  user = Sys.getenv("ZOTERO_ID"),
  key = Sys.getenv("ZOTERO_KEY"),
  collection = Sys.getenv("ZOTERO_REVIEW")
)

bib_list(reviews, "review")
```

### Technical reports

```{r}
#| label: reports
reports <- get_collection(
  user = Sys.getenv("ZOTERO_ID"),
  key = Sys.getenv("ZOTERO_KEY"),
  collection = Sys.getenv("ZOTERO_REPORT")
)

bib_list(reports, "report")
```

## {{< iconify fa6-solid:hand-holding-dollar >}} Grants, Fellowships, and Awards

```{r}
#| label: funding
funding <- read_sheet(Sys.getenv("GOOGLE_PAGE_ID"), sheet = "funding") |>
  subset(result == "Awarded") |>
  transform(collection = "Funding")

bib_list(funding, "funding")
```

## {{< iconify fa6-solid:desktop >}} Presentations

```{r}
#| label: presentations
presentations <- get_collection(
  user = Sys.getenv("ZOTERO_ID"),
  key = Sys.getenv("ZOTERO_KEY"),
  collection = Sys.getenv("ZOTERO_PRESENTATION")
)

bib_list(presentations, "presentation")
```

## {{< iconify fa-solid:chalkboard-teacher >}} Teaching {#teaching}

::: {.mb-2}
**Teaching interests**. Behavioral Ecology, Urban Science, Environmental Data 
Science, Statistics, Geography, Conservation & Sustainability, Human Prehistory, 
North American Prehistory.
:::

**University of Utah**  

-   ANTH 1010: Culture and the Human Experience  
-   ANTH 1030: Introduction to World Prehistory  
-   ANTH 5850: Quantitative Analysis of Archaeological Data  

## {{< iconify fa6-solid:people-arrows >}} Professional Affiliations

::: {.about-list}
-   [**Great Basin Anthropological
    Association**](https://greatbasinanthropologicalassociation.org/) |
    2016-present  
-   [**Society for American Archaeology**](https://www.saa.org/) | 2014-present  
-   [**Coalition for Archaeological Synthesis**](https://www.archsynth.org/) |
    2022-present  
-   [**European Association of Archaeologists**](https://www.e-a-a.org/) |
    2023-present  
:::

## {{< iconify fa-solid:hands-helping >}} Service, Outreach, and Other Activities

::: {.about-list}
-   **Studio Lab** | University of Colorado, Boulder, 2022-2024.  
    {{< iconify tabler:checklist >}} **Mentor**. Supporting undergraduate research.  
-   **Undergraduate Research Opportunities Program**. | University of Utah, 2018-2022.  
    {{< iconify tabler:checklist >}} **Mentor**. Supporting undergraduate research.  
-   **Journal Club: Problems in Evolutionary Anthropology** | University of Utah, 2018-2022.  
    {{< iconify tabler:checklist >}} **Organizer**.  
-   **Hopi Tribe v Donald J. Trump, Utah Diné Bikéyah v Donald J. Trump, Natural 
    Resources Defense Council v Donald J. Trump** | 2018.  
    Brief Amici Curiae of Archaeological Organizations in Support of Plaintiffs.  
    {{< iconify tabler:checklist >}} **Contributor**.  
:::

## {{< iconify fa6-solid:envelope >}} References

*Available upon request.*