---
title: "Curriculum Vitae"
---

<!-- To embed Academicicons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">

```{r, include = FALSE}
source("setup.R")
source("cv_tables.R")
```

```{r}

collection <- here("data", "collections") %>% jsonlite::read_json(simplifyVector = TRUE)

zotero <- here("data", "zotero") %>% jsonlite::read_json(simplifyVector = TRUE)

bib <- cv_get_bib(zotero, collection)

```


<div style = "font-size: 14px;"> 
_For a pdf of my curriculum vitae, click the CV button in the navbar._  
</div>


<br>

### Contact information  

Department of Anthropology  
University of Utah  
260 Central Campus Drive  
Salt Lake City, UT 84112  
(801) 581-6252  
[faculty.utah.edu/~kbvernon](https://faculty.utah.edu/~kbvernon)

<br>

### Appointments

```{r}

here("data", "appointments.csv") %>% 
  read.csv() %>% 
  mutate(x = glue::glue("{title}, {organization}"), 
         y = case_when(is.na(end) ~ glue::glue("{start}-present"),
                       TRUE ~ glue::glue("{start}-{end}"))) %>% 
  select(x, y) %>% 
  cv_kable()

```

<br>

### Education 

```{r}

here("data", "education.csv") %>% 
  read.csv() %>% 
  mutate(x = glue::glue("<b>{university}</b><br>{degree} in {major}"), 
         y = glue::glue("{location}<br>{end}")) %>% 
  select(x, y) %>% 
  cv_kable()

```

<br>

### Publications

See the [publications](./publications.html) page.

<br>

### Grants, Fellowships, and Awards

```{r}

here("data", "funding.csv") %>% 
  read.csv() %>% 
  filter(result == "Awarded") %>% 
  arrange(desc(year)) %>% 
  mutate(y = glue::glue("{FOT}, {organization}. \"{title}\". PI: {PI}.<br><br>")) %>% 
  select(year, y) %>% 
  cv_bibble()

```

<br>

### Presentations

```{r}

bib %>% 
  filter(groups == "Presentation") %>% 
  mutate(ref = glue::glue("{author} ({year}). {title}. _{type} at the {shorttitle}, {address}_.<br><br>")) %>% 
  select(year, ref) %>% 
  cv_bibble()

```

<br>

### Teaching

_Teaching interests_:  

<div style = "text-align: justify; text-justify: inter-word;">
Behavioral Ecology, Human Ecology, Human Prehistory, Hunter-Gatherers, Conservation \& Sustainability, Ethnoarchaeology, GIS/Spatial Analysis, Quantitative Data Analysis, Archaeological Method \& Theory, North American Prehistory  
</div>

_University of Utah, Department of Anthropology_:  

```{r, results = "asis"}

here("data", "teaching.csv") %>% 
  read.csv() %>% 
  glue_data("* {x}  ", x = unique(course))

```

<br>

### Professional Affiliations

```{r}

here("data", "affiliations.csv") %>% 
  read.csv() %>% 
  mutate(x = glue("<a href='{url}' target='_blank'>{organization}</a>"), 
         y = glue("{start}-{end}")) %>% 
  select(x, y) %>% 
  cv_kable()

```