---
title: "Curriculum Vitae"
---

```{r, include = FALSE}

source("setup.R")

```

<div style = "font-size: 14px;"> 
_To download a PDF of my curriculum vitae, click the CV button in the navbar._  
</div>

### `r fa("address-card")` Contact information  

Department of Anthropology  
University of Utah  
260 Central Campus Drive  
Salt Lake City, UT 84112  
(801) 581-6252  
[faculty.utah.edu/~kbvernon](https://faculty.utah.edu/~kbvernon)

### `r fa("briefcase")` Appointments

```{r}

read_sheet(google_page_id, sheet = "appointments")  %>%
  mutate(
    x = glue::glue("{title}, {organization}"),
    y = ifelse(
      is.na(end), 
      glue::glue("{start}-present"),
      glue::glue("{start}-{end}")
    )
  ) %>% 
  select(x, y) %>% 
  kbl(
    escape = FALSE,
    col.names = NULL,
    align = c('l', 'r'),
    table.attr = "class='cv-table'"
  ) %>%
  kable_styling(full_width = TRUE) %>%
  collapse_rows(columns = 1, valign = "top")

```

### `r fa("graduation-cap")` Education

```{r}

read_sheet(google_page_id, sheet = "education") %>% 
  mutate(
    x = glue::glue("__{university}__<br>{degree} in {major}"), 
    y = glue::glue("{location}<br>{end}")
  ) %>% 
  select(x, y) %>% 
  kbl(
    escape = FALSE,
    col.names = NULL,
    align = c('l', 'r'),
    table.attr = "class='cv-table'"
  ) %>%
  kable_styling(full_width = TRUE) %>%
  collapse_rows(columns = 1, valign = "top")

```

### `r fa("book")` Publications

See the [publications](./publications.html) page.

### `r fa("hand-holding-usd")` Grants, Fellowships, and Awards {#funding}

```{r}

read_sheet(google_page_id, sheet = "funding") %>% 
  filter(result == "Awarded") %>% 
  mutate(
    item = glue::glue(
      
      "{FOT}, {organization}. <b>{title}</b>. PI: {PI}."
  
    )) %>% 
  make_ordered_list()

```

### `r fa("desktop")` Presentations

```{r}

bib %>% 
  filter(groups == "Presentation") %>% 
  mutate(
    item = glue::glue(
      
      "{author} ({year}). {title}. _{type} at the {shorttitle}, {address}_."
      
    )) %>% 
  make_ordered_list()

```

### `r fa("chalkboard-teacher")` Teaching {#teaching}

__Teaching interests__. Behavioral Ecology, Human Ecology, Human Prehistory, Hunter-Gatherers, Conservation \& Sustainability, Ethnoarchaeology, GIS/Spatial Analysis, Quantitative Data Analysis, Archaeological Method \& Theory, North American Prehistory  

```{r}

read_sheet(google_page_id, sheet = "teaching") %>% 
  group_by(university, department) %>% 
  summarize(
    courses = paste0("<li>", unique(course), "</li>", collapse = "\n")
  ) %>% 
  rowwise() %>% 
  mutate(
    teaching = glue::glue(
      
      "<p>{university}, Department of {department}</p><ul>{courses}</ul>"
      
    ),
  ) %>% 
  pull(teaching) %>% 
  paste("<div class = 'cv-teaching'>", ., "</div>") %>% 
  cat()

```

### `r fa("people-arrows")` Professional Affiliations {#affiliations}

```{r}

read_sheet(google_page_id, sheet = "affiliations") %>% 
  mutate(
    x = glue::glue("<a href='{url}'>{organization}</a>"), 
    y = glue::glue("{start}-{end}")
  ) %>% 
  select(x, y) %>% 
  kbl(
    escape = FALSE,
    col.names = NULL,
    align = c('l', 'r'),
    table.attr = "class='cv-table'"
  ) %>%
  kable_styling(full_width = TRUE) %>%
  collapse_rows(columns = 1, valign = "top")

```