---
title: vitae
author: K.B. Vernon
date: '2020-04-07'
slug: vitae
categories: []
tags: []
description: ''
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

library(glue)
library(here)
library(icon) # github only (ropenscilabs)
library(jsonlite)
library(kableExtra)
library(knitr)
library(RefManageR)
library(tidyverse)

options(knitr.kable.NA = "")

```

```{r}

source(here("style/blake_cv_style.R"))

```

```{r}

collection <- jsonlite::read_json(here("data/collections"), simplifyVector = TRUE)

zotero <- jsonlite::read_json(here("data/zotero"), simplifyVector = TRUE)

bib <- cv_bibble(zotero, collection)

```


<div style = "font-size: 14px;"> 
_For a pdf of my curriculum vitae, click the CV button in the navbar._  
</div>


<br>

### Contact information  

Department of Anthropology  
University of Utah  
260 Central Campus Drive  
Salt Lake City, UT 84112  
(801) 581-6252  
<a href="https://faculty.utah.edu/~kbvernon" target="_blank">faculty.utah.edu/~kbvernon</a>  

<br>

***

<br>

### Appointments

```{r}

read.csv(here("data/appointments.csv"), stringsAsFactors = FALSE) %>% 
  mutate(x = glue::glue("{title}, {organization}"), 
         y = case_when(is.na(end) ~ glue::glue("{start}-present"),
                       TRUE ~ glue::glue("{start}-{end}"))) %>% 
  select(x, y) %>% 
  cv_kable()

```

<br>

***

<br>

### Education 

```{r}

read.csv(here("data/education.csv"), stringsAsFactors = FALSE) %>% 
  mutate(x = glue::glue("<b>{university}</b><br>{degree} in {major}"), 
         y = glue::glue("{location}<br>{end}")) %>% 
  select(x, y) %>% 
  cv_kable()

```

<br>

***

<br>

### Grants, Fellowships, and Awards

```{r}

read.csv(here("data/funding.csv"), stringsAsFactors = FALSE) %>% 
  filter(result == "Awarded") %>% 
  arrange(desc(year)) %>% 
  mutate(y = glue::glue("{FOT}, {organization}. \"{title}\". PI: {PI}.<br><br>")) %>% 
  select(year, y) %>% 
  cv_kable(bib = TRUE)

```

<br>

***

<br>

### Presentations

```{r}

bib %>% 
  filter(groups == "Presentation") %>% 
  mutate(ref = glue::glue("{author} ({year}). {title}. _{type} at the {shorttitle}, {address}_.<br><br>")) %>% 
  select(year, ref) %>% 
  cv_kable(bib = TRUE)
  
```

<br>

***

<br>

### Teaching

_Teaching interests_:  

<div style = "text-align: justify; text-justify: inter-word;">
Behavioral Ecology, Human Ecology, Human Prehistory, Hunter-Gatherers, Conservation \& Sustainability, Ethnoarchaeology, GIS/Spatial Analysis, Quantitative Data Analysis, Archaeological Method \& Theory, North American Prehistory  
</div>

_University of Utah, Department of Anthropology_:  

```{r, results = "asis"}

read.csv(here::here("data/teaching.csv"), stringsAsFactors = FALSE) %>% 
  glue::glue_data("* {x} <br>", x = unique(course))

```

<br>

***

<br>

### Professional Affiliations

```{r}

read.csv(here("data/affiliations.csv"), stringsAsFactors = FALSE) %>% 
  mutate(x = glue::glue("<a href='{url}' target='_blank'>{organization}</a>"), 
         y = glue::glue("{start}-{end}")) %>% 
  select(x, y) %>% 
  cv_kable()

```
